Gap formation and stability in non-isothermal protoplanetary discs

### 2015-03-27 paper/summary.tex
fixed versions

{\bf For our main simulations with $\tilde{\beta}\geq 0.1$}, the duration of the quasi-steady state increases with
increasing cooling timescales until a critical value, beyond which this
quasi-steady state shortens again. {\bf We find the timescale for the vortex to
decay, after reaching maximum amplitude, can be long for small
$\tilde{\beta}$ which contributes to a long overall vortex lifetime
with rapid cooling.} We do observe vortex migration during {\bf its}
decay, which may influence this decay timescale.

>>>>

{\bf For our main simulations with $\tilde{\beta}\geq 0.1$}, the duration of the quasi-steady state increases with
increasing cooling timescales until a critical value, beyond which this
quasi-steady state shortens again. {\bf We find the timescale for the vortex to
decay after reaching maximum amplitude can be long for small
$\tilde{\beta}$, which contributes to a long overall vortex lifetime
with rapid cooling.} We do observe vortex migration during {\bf its}
decay, which may influence this decay timescale.
